Trans-Dimensional Inference for Gravitational Lens Substructures

### 2015-06-10 Papers/ms.tex
Abstract and acknowledgement work

\begin{abstract}

\end{abstract}

@@

\begin{table*}
\begin{tabular}{|l|l|l|}
\hline
Quantity	&	Meaning		& Prior\\
\hline
{\bf Hyperparameters}\\
$N_{\rm src}$	&	Number of source blobs	& Uniform($0, 1, ..., 100$)\\
$N_{\rm lens}$	&	Number of lens blobs	& Uniform($0, 1, ..., 10$)\\
$(x_c^{\rm src}, y_c^{\rm src})$ & Typical position of source blobs & \\
$(x_c^{\rm lens}, y_c^{\rm lens})$ & Typical position of lens blobs &\\
$R_{\rm src}$   &	Typical distance of source blobs from $(x_c^{\rm src}, y_c^{\rm src})$ & \\
$R_{\rm lens}$  &	Typical distance of lens blobs from $(x_c^{\rm lens}, y_c^{\rm lens})$ 	& \\
$\mu_{\rm src}$ &	Typical flux of source blobs	& \\
$\mu_{\rm lens}$&	Typical mass of lens blobs	& \\
$W_{\rm src}$ &		Typical width of source blobs	& \\
$W_{\rm lens}$&		Typical width of lens blobs	& \\
{\bf Lens Blob Parameters}\\
{\bf Source Blob Parameters}\\
{\bf Smooth Lens Parameters}\\
{\bf Noise Parameters}\\
{\bf Data}\\
\end{tabular}
\caption{All of the prior distributions.
\label{tab:priors}}
\end{table*}

@@

>>>>

\begin{abstract}
We introduce a Bayesian solution to the problem of inferring the density
profile of strong gravitational lenses when the lens galaxy may contain
multiple dark or faint substructures. The source and lens models are based on
a superposition of an unknown number of non-negative basis functions
(or ``blobs'') which were chosen with speed as a primary criterion.
The prior distribution for the blobs' properties is specified hierarchically,
so the ``mass function'' of substructures is a natural output. We use reversible
jump Markov Chain Monte Carlo (MCMC) within Diffusive Nested Sampling (DNS) to
sample the posterior distribution and evaluate the marginal likelihood of the
model. We demonstrate the method on a simulated data set, and also apply it to
the Cosmic Horseshoe, finding ...
\end{abstract}

@@

\begin{table*}
\begin{tabular}{|l|l|l|}
\hline
Quantity	&	Meaning		& Prior\\
\hline
{\bf Hyperparameters}\\
$N_{\rm src}$	&	Number of source blobs	& Uniform($0, 1, ..., 100$)\\
$N_{\rm lens}$	&	Number of lens blobs	& Uniform($0, 1, ..., 10$)\\
$(x_c^{\rm src}, y_c^{\rm src})$ & Typical position of source blobs & \\
$(x_c^{\rm lens}, y_c^{\rm lens})$ & Typical position of lens blobs &\\
$R_{\rm src}$   &	Typical distance of source blobs from $(x_c^{\rm src}, y_c^{\rm src})$ & \\
$R_{\rm lens}$  &	Typical distance of lens blobs from $(x_c^{\rm lens}, y_c^{\rm lens})$ 	& \\
$\mu_{\rm src}$ &	Typical flux of source blobs	& \\
$\mu_{\rm lens}$&	Typical mass of lens blobs	& \\
$W_{\rm src}$ &		Typical width of source blobs	& \\
$W_{\rm lens}$&		Typical width of lens blobs	& \\
{\bf Lens Blob Parameters}\\
$(x_i^{\rm src}, y_i^{\rm src})$
$M_i$  &
$v_i$  &
{\bf Source Blob Parameters}\\
{\bf Smooth Lens Parameters}\\
{\bf Noise Parameters}\\
{\bf Data}\\
\end{tabular}
\caption{All of the prior distributions.
\label{tab:priors}}
\end{table*}

@@

\section*{Acknowledgements}
It is a pleasure to thank ...

This work was funded by a Marsden Fast Start grant from the Royal Society of
New Zealand.
